### 2016-05-29 w-wires/paper_gerasimovda.tex
More proof in paper

\DeclareMathOperator\atanh{atanh}
\DeclareMathOperator\atan{atan}

@@

Fox the computational convenience, it $C_r$ is parameterized via $k = R(r) \eexp{\iu t} + \iu C(r)$, which yields us the final form of the criterion, which we will use further:

@@

% TODO
% https://proofwiki.org/wiki/Inverse_of_Strictly_Increasing_Strictly_Concave_Real_Function_is_Strictly_Convex
Since $s_1$ is concave \todo{proof? just take a look at second derivative?}, strictly increasing and for fixed $r$, our domain of interest is only $\Im k \le C + R$, we can approximate the function by a linear function $s_4$.

@@

>>>>

\DeclareMathOperator\atanh{atanh}
\DeclareMathOperator\atan{atan}
\DeclareMathOperator\asin{asin}

@@

For the computational convenience, $C_r$ is parameterized via $k = R(r) \eexp{\iu t} + \iu C(r)$, which yields us the final form of the criterion, which we will use further:

@@

% TODO
% https://proofwiki.org/wiki/Inverse_of_Strictly_Increasing_Strictly_Concave_Real_Function_is_Strictly_Convex
 % \todo{proof? just take a look at second derivative?}
Since $s_1$ is concave, strictly increasing and for fixed $r$, our domain of interest is only $\Im k \le C + R$, we estimate the function from below by a linear function $s_4$:

@@

\todo{full circle; explain what is $\phi$}
\begin{align*}
    & \int\limits_{t = \phi}^{\frac{\pi}{2}} \ln^2 s(R \eexp{\iu t} + \iu C) \frac{R}{\norm{R \eexp{\iu t} + \iu C + i}^2} dt\\
=   & \int\limits_{t = \phi}^{\frac{\pi}{2}} \ln^2 f(R \sin t + C) \frac{R}{R^2 \cos^2 t + (R \sin t + C + 1)^2} dt\\
\le & \int\limits_{t = \phi}^{\frac{\pi}{2}} \ln^2 f(R \sin t + C) \frac{R}{R^2 \cos^2 t + (R \sin t + C)^2} dt\\
\end{align*}

Change of variables:

\begin{align*}
y &= R \sin t + C \\
t &= \asin \frac{y - C}{R} \\
dt &= \frac{1}{\sqrt{R^2 - (C - y)^2}} dy \\
\cos t &= \frac{\sqrt{R^2 - (C - y)^2}}{R}
\end{align*}

\begin{align*}
    & \int\limits_{y = Z}^{R + C} \ln^2 f(y) \frac{R}{R^2 \cos^2 t + (R \sin t + C)^2} dy \\
=   & \int\limits_{y = Z}^{R + C} \ln^2 f(y) \frac{R}{R^2 - (C - y)^2 + y^2} \frac{1}{\sqrt{R^2 - (C - y)^2}} dy\\
=   & \int\limits_{y = Z}^{R + C} \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 C y} \frac{1}{\sqrt{(R - C + y)}} \frac{1}{\sqrt{(R + C - y)}} dy\\
\end{align*}

To estimate, we will split the integration in two parts: from $Z$ to $C$ and from $C$ to $R + C$.

\todo{first part}

Second part:

\begin{align*}
    & \int\limits_{y = C}^{R + C} \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 C y} \frac{1}{\sqrt{(R - C + y)}} \frac{1}{\sqrt{(R + C - y)}} dy\\
\le & \int\limits_{y = C}^{R + C} \ln^2 f(C) \frac{R}{R^2 - C^2 + 2 C C} \frac{1}{\sqrt{(R - C + C)}} \frac{1}{\sqrt{(R + C - y)}} dy\\
=   & \ln^2 f(C) \frac{R}{R^2 + C^2} \frac{1}{\sqrt{R}} \int\limits_{y = C}^{R + C} \frac{1}{\sqrt{R + C - y}} dy\\
=   & \ln^2 f(C) \frac{R}{R^2 + C^2} \frac{1}{\sqrt{R}} 2 \sqrt{R}\\
\end{align*}
\todo{show that logarithmic part is constant, that finishes the proof}

\begin{align*} 
    & \int\limits_{y = Z}^{C} \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 C y} \frac{1}{\sqrt{(R - C + y)}} \frac{1}{\sqrt{(R + C - y)}} dy\\
\le & \int\limits_{y = Z}^{C} \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 C y} \frac{1}{\sqrt{(R - C + Z)}} \frac{1}{\sqrt{(R + C - C)}} dy\\
=   & \frac{1}{\sqrt{R - C + Z}} \frac{R}{\sqrt{R}}  \int\limits_{y = Z}^{C} \ln^2 f(y) \frac{1}{R^2 - C^2 + 2 C y} dy\\
\end{align*}

\todo{ugh, estimate via $\int \ln^2(a x + b) \frac{1}{c x + d}$? }
